---
title: "Extra Credit Project"
author: "Marc Luiz, Nelly Shieh, Jeff Nguyen"
date: "18/09/2020"
output:
  pdf_document: default
  html_document:
    code_folding: "hide"
  word_document: default
---
```{r include = FALSE}
#knitr::opts_chunk$set(echo=FALSE)
```

**Coitegration Analysis of Different Financial Markets**  
**University of Southern California**  
**Marshall School of Business**  
**FBE 543 Forecasting and Risk Analysis**  
**Spring 2021**  
**Directed by Professor Mohammad Safarzadeh**   
  
# Topic:  
Using major stock indices for the United States (S&P500), Unite Kingdom (FTSE100), Germany (DAX), and France (CAC40) show that US and European financial markets conintegrate.  

# Method:  
**Reviewing cointegration condition:**    

Consider 2 time series variables $Y$ and $X$. We have the regression equation as follow:  

\begin{equation}
  \begin{aligned}
    Y_t =& \beta_0 + \beta_1 X_t + \epsilon_t  \\
  \end{aligned}
\end{equation}
  
The cointegration is such that if $X$ and $Y$ are both non-stationary variables AND $\epsilon$ is a stationary variable, then $X$ and $Y$ cointegrate, i.e. they "move together" in the long run.  

Thus, our primary methodology is as follow:  

## 1. Test indices for stationarity:  
Test representative stock indices in the United States (S&P 500), the United Kingdom (FTSE), Germany (DAX) and France (CAC40) for stationarity.  
To execute this task, for each indices, we run the Augmented Dickey-Fuller Test (A)DF, which hypothesizes that a unit root is present in an autoregressive model. The intuition is such that if a variable is stationary, it tends to a constant mean--i.e. the values oscillates/ alternate for large to small. As a result, the process is not a random walk, i.e. nonstationary.

## 2. Test error term for stationarity:  
Should the regressed result confirm non-stationarity, check whether the error term of the regression $\epsilon$ are non-stationary variables. If they are, then the indices cointegrate.  
  
First we check for the common issue with time series data: positive autocorrelation by running Durbin-Watson Test. If autocorrelation exists, we add the first order autoregressive term $AR(1)$ into the model and subsequently $AR(2)$ as necessary.

Then, we run (A)DF test as above to test the error term for stationarity--not having a unit root in the (A)DF test.  

# Data Analysis  

For this model, we use 20 years of data from March 2001 to March 2021.  

Downloading data:  

```{r}
```
tbc